\sc Cells at War: The Playfulness of Game-Based Learning

### 2023-03-14 thesis_template/paper0904.tex
Results inputted into paper, start writing now

\documentclass{article}
%\documentclass[twocolumn]{article}
%\documentclass[onecolumn]{article}
% \usepackage{scrtime} % for \thistime (this package MUST be listed first!)
\DeclareUnicodeCharacter{0301}{\'{e}}
\usepackage{times}
\usepackage{graphicx}
\usepackage{float}
\usepackage[margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage{caption}
\usepackage{notoccite}
\usepackage{pgfplotstable}
%\usepackage[round]{natbib}
%\setcitestyle{aysep={}} %removes the comma between the author and year in citations
%\usepackage{underscore}
\usepackage{pdfpages}
\usepackage{xcolor,colortbl}%for changing cell colour
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{capt-of}
\pagestyle{fancy}
\setlength{\headheight}{15.2pt}
\setlength{\headsep}{13 pt}
\setlength{\parindent}{28 pt}
\setlength{\parskip}{12 pt}
\pagestyle{fancyplain}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
% \usepackage{color,amsmath,amssymb,amsthm,mathrsfs,amsfonts,dsfont}
\usepackage{xspace}
\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{calc, arrows}
\usetikzlibrary{external}
\usepackage{pgfplots}
\pgfplotsset{layers/my layer set/.define layer set={background,main,foreground}{},
        set layers=my layer set,}

@@

\lhead{Cells at War: Game-Based Learning} %This needs to change
\rhead{Bianca Flaim, Alexander Turco}
\title{\sc Cells at War: The Playfulness of Game-Based Learning}
\author{\sc Bianca Flaim, Alexander Turco and Rosa da Silva}

@@

In 2021, the BIO1A03 instructional team partnered up with the George Brown College School of Design, and received support from CEWIL Canada (Co-operative Education and Work-Integrated Learning Canada), formerly known as CAFCE (Canadian Association for Co-operative Education), to design and implement an educational biological video game that could be used as an instructional and engaging teaching tool in BIO1A03. A small cohort of McMaster Univeristy Biology students and supervising professors, as well as game designers, programmers, animators, audio engineers, and artists from the George Brown College School of Design were selected to pilot this project.

@@

\subsection{Survey Design: Qualitative Analysis of Student Feedback}

@@

@@

>>>>

\documentclass{article}
%\documentclass[twocolumn]{article}
%\documentclass[onecolumn]{article}
% \usepackage{scrtime} % for \thistime (this package MUST be listed first!)
\DeclareUnicodeCharacter{0301}{\'{e}}
\usepackage{float}
\usepackage{times}
\usepackage{graphicx}
\usepackage{float}
\usepackage[margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage{caption}
\usepackage{notoccite}
\usepackage{pgfplotstable}
%\usepackage[round]{natbib}
%\setcitestyle{aysep={}} %removes the comma between the author and year in citations
%\usepackage{underscore}
\usepackage{pdfpages}
\usepackage{xcolor,colortbl}%for changing cell colour
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{capt-of}
\pagestyle{fancy}
\setlength{\headheight}{15.2pt}
\setlength{\headsep}{13 pt}
\setlength{\parindent}{28 pt}
\setlength{\parskip}{12 pt}
\pagestyle{fancyplain}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
% \usepackage{color,amsmath,amssymb,amsthm,mathrsfs,amsfonts,dsfont}
\usepackage{xspace}
\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{calc, arrows}
\usetikzlibrary{external}
\usepackage{pgfplots}
\pgfplotsset{layers/my layer set/.define layer set={background,main,foreground}{},
        set layers=my layer set,}

@@

\lhead{Cells at War: Game-Based Learning} %This needs to change
\rhead{Bianca Flaim, Alexander Turco}
\title{\sc Cells at War: The Playfulness of Game-Based Learning}
\author{\sc Alexander Turco and Rosa da Silva}

@@

In 2021, the BIO1A03 instructional team partnered up with the George Brown College School of Design, and received support from CEWIL Canada (Co-operative Education and Work-Integrated Learning Canada), formerly known as CAFCE (Canadian Association for Co-operative Education), to design and implement an educational biological video game that could be used as an instructional and engaging teaching tool in BIO1A03. A small cohort of McMaster Univeristy Biology students and supervising professors, as well as game designers, programmers, animators, audio engineers, and artists from the George Brown College School of Design were selected to pilot this work-integrated learning project.

@@

\subsection{Survey Design: Qualitative Analysis of Student Feedback NOT DONE YET}

@@

\subsection{Student perceptions of current undergraduate experiences}

150 students enrolled in the winter 2021 session of BIO1A03 attended a game-based style lecture and completed the follow-up survey. Participants were asked a series of questions regarding their current experiences as undergraduate science students, as well as questions regarding the benefits of implementing game-based learning approaches into their classrooms.

%%%%%TIME SPENT PLAYING VIDEO GAMES
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/time_spent_playing_videogames.jpg}
	\caption{Student responses regarding the average amount of weekly time spent playing video games}
	\label{fig:1}
\end{figure}

%%%%%Types of courses taken by students
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/types_of_courses_taken.jpg}
	\caption{Types of Courses Taken}
	\label{fig:2}
\end{figure}

%%%%%During the current school year how much has your coursework emphasized the following
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/howmuch_coursework_emphasized_thefollowing.jpg}
	\caption{How Much Has Coursework Emphasized the following}
	\label{fig:3}
\end{figure}

%%%%%During the current school year how often would you say you have done the following
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_often_haveyou_done_thefollowing.jpg}
	\caption{How often have you done the following}
	\label{fig:4}
\end{figure}

\subsection{Student perceptions on the use of game-based learning in biology}

%%%%%If game-based learning approaches were incorporated into one of your science courses, how do you think that this mode of learning can help with the following
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_does_gbl_help_in_science.jpg}
	\caption{If game-based learning approaches were incorporated in your science courses}
	\label{fig:5}
\end{figure}

%%%%% If BIO1A03 added a game-based learning component, how much would this improve your motivation to do the following?
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/ifbio1a03_added_gblcomponent.jpg}
	\caption{If BIO1A03 added a game-based component}
	\label{fig:6}
\end{figure}

%%%%% How likely is it that you would play the video game Cells at War on your own time, outside of class to further consolidate material taught during this class
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_likely_you_would_play_cellsatwar.jpg}
	\caption{How likely is it you would play Cells at War outside of class}
	\label{fig:7}
\end{figure}

%%%%%How prepared would you feel if you were given a quiz on Pompe Disease based on the Cells at War game, compared to studying off traditional lecture slides
\begin{figure}[H]
	\includegraphics[width=\textwidth]{figures_4f06/how_prepared_if_tested_on_pompe_based_off_cellsatwar.jpg}
	\caption{How prepared would you feel if given a quiz on Pompe Disease}
	\label{fig:8}
\end{figure}

@@

We need to highlight in this section the use of Cells at War as an instructional tool as well as the benefits that students get out of this work integrated learning experience
